%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -- Evan Steele --
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, oneside, final]{scrartcl} % Paper options using the scrartcl class

\usepackage{scrpage2} % Provides headers and footers configuration
\usepackage{fontawesome} % for social media logos
\usepackage{fontspec}
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{marvosym} % Allows the use of symbols
\usepackage{tabularx,colortbl} % Advanced table configurations
\usepackage{fontspec} % Allows font customization
\usepackage{tikz}
\usepackage{hyperref}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont{"[adobe_garamond.ttf]"} % Main document font

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\pagestyle{scrheadings} % Print the headers and footers on all pages

\addtolength{\voffset}{-0.2in} % Adjust the vertical offset - less whitespace at the top of the page
\addtolength{\textheight}{3cm} % Adjust the text height - less whitespace at the bottom of the page

\newcommand{\gray}{\rowcolor[gray]{.90}} % Custom highlighting for the work experience and education sections

%----------------------------------------------------------------------------------------
% FOOTER SECTION
%----------------------------------------------------------------------------------------

\renewcommand{\headfont}{\normalfont\rmfamily\scshape} % Font settings for footer

\cofoot{
\addfontfeature{LetterSpace=20.0}\fontsize{12.5}{12}\selectfont % Letter spacing and font size

4051 Kensington Drive {\large\textperiodcentered} Concord {\large\textperiodcentered} California\\ % Your mailing address
{\Large\Letter} keeganseck@gmail.com {\Large\Telefon} (925) 586-8095 \\
\faLinkedin \space \href{https://www.linkedin.com/pub/evan-steele/83/1b7/b43}{Keegan Seck} \faYoutubePlay \space \href{https://www.youtube.com/channel/UCWcdZhwDnRL\_jbgaRI7tAGA}{Channel}
} % Your email address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center} % Center everything in the document

%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------

{\addfontfeature{LetterSpace=20.0}\fontsize{20}{16}\selectfont\scshape Keegan Seck}\\ % Your name at the top

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\section{Objective}
As a recent graduate of the UCSC Film and Digital Media degree program, I am well equipped for professional media production in any capacity. My education provides me with strong technical skills in film editing, where my experience with programs such as Adobe Premiere creates high-quality, professional content. Additionally, I worked in large teams to collaborate on complex film projects, leading teams with my strong direction and organization skills. My long-term goal is to join a film or television production company to bring my powerful skill set and unique vision into the digial media age.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}


\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{September 2012 --- March 2017}\\
\gray Degree & \textbf{Bachelor of Arts in Film and Digital Media, Production Concentration}\\
\gray University & \textbf{University of California Santa Cruz} \hfill Santa Cruz, California\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	Writing& Developed strong writing abilities for film and digital media. Proficient technical and creative skills, with effective use of feedback.\\
\arrayrulecolor{gray}\hline
	Technical Editing& Experience with Adobe Premiere for university projects. Worked alongside other students to create professional content.\\
\arrayrulecolor{gray}\hline
	Filmmaking & Worked with audio and visual equipment for film production, including proficient camera work.\\
\arrayrulecolor{gray}\hline
	Computer Skills& Working skills with enterprise computer processes and services. Experience with programming languages with a large capacity for learning.\\
\arrayrulecolor{gray}\hline
	Organization & Years of experience working with complicated organizations and groups. Understands effective group interaction and team management.\\
\arrayrulecolor{gray}\hline
\end{tabularx}

%----------------------------------------------------------------------------------------


\end{center}

\end{document}
